Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-16 writing/embedded_meta_learning.tex
Astronomy part II

For example, if the $z_{old}$ is the system's embedding for trying to win at go, and the meta-dataset consists of examples of a winning strategy and a losing strategy for different games, then $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go. We could then evaluate how well the system actually loses with the $\hat{z}_{new}$ strategy. \par
Similarly, we could map from language to a task embedding, and then evaluate the system at the specified task. The key feature of our architecture -- the fact that tasks, data, and language are all embedded in a shared space -- allows substantial flexibility within a unified framework.

@@

\caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings, either from examples (\subref{poly_meta_map_results_examples}) or from language cues (\subref{poly_meta_map_results_language}). This shows the loss produced when evaluating the mapped embedding on the target task. For example, if the initial polynomial is $p(x) = x + 1$, and the meta-task is ``square,'' the loss would be evaluated by taking the embedding produced by applying this meta-mapping to the embedding of $f(x)$ and evaluating how the mapped embedding regresses $p(x)^2 = x^2 + 2x + 1$. The solid line indicates optimal performance; the dashed line indicates chance (untrained). Error-bars are bootstrap 95\%-CIs.} 

@@

\paragraph{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior, as shown in fig. \ref{poly_meta_map_results}. We train the system to perform a variety of mappings, for example switch the first two inputs of the polynomial, add 3 to the polynomial, or square the polynomial. We then test its ability to generalize to held-out mappings, for example a permutation of the polynomial inputs which it has not encountered before, or an additive shift in the polynomial which it has not been trained on. The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of their application or receiving a natural-language instruction. However, it generalizes better to new meta-mappings from examples than language, which is not completely surprising, since the examples provide a richer dataset to learn from. \par 

@@

\paragraph{Conclusions:} In this paper, we've highlighted a new type of flexibility in the form of \emph{meta-mappings}, that is, mappings between tasks. We've suggested that achieving this type of flexibility is difficult in most deep learning architectures, because they separate computation from the knowledge of what is being computed. To address this, we've proposed explicitly representing the tasks by embeddings, and deriving the computation from these embeddings via a HyperNetwork. This allows transformations over task embeddings to transform the system's behavior. To this end, we've proposed a meta-learning system which embeds tasks and data into a shared latent space, and then meta-learns to make mappings over this space. The requisite meta-task sample complexity is small; we showed generalization to unseen meta-mappings after training on only 20 meta-mappings.\par

@@

>>>>

For example, if the $z_{old}$ is the system's embedding for trying to win at go, and the meta-dataset consists of examples of a winning strategy and a losing strategy for different games, then $\hat{z}_{new}$ could be interpreted as the system's guess at a losing strategy for go. We could then evaluate how well the system actually loses with the $\hat{z}_{new}$ strategy. All meta-mapping results reported here were evaluated in that way -- evaluating the loss on the target task after transforming the function embedding. \par
Alternatively, we could map from language to a meta-mapping embedding, rather than inducing it from examples of the meta-mapping. This corresponds to the human ability to change behavior in response to instructions. The key feature of our architecture -- the fact that tasks, data, and language are all embedded in a shared space -- allows for substantial flexibility within a unified framework.

@@

\caption{The system generalizes to apply learned meta-mappings to new tasks, and to apply unlearned meta-mappings, either from examples (\subref{poly_meta_map_results_examples}) or from language cues (\subref{poly_meta_map_results_language}). The plots show the loss produced when evaluating the mapped embedding on the target task. For example, if the initial polynomial is $p(x) = x + 1$, and the meta-task is ``square,'' the loss would be evaluated by taking the embedding produced by applying this meta-mapping to the embedding of $p(x)$ and evaluating how well the mapped embedding regresses $p(x)^2 = x^2 + 2x + 1$. The solid line indicates optimal performance; the dashed line indicates chance (untrained). Error-bars are bootstrap 95\%-CIs.} 

@@

\paragraph{Meta mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings (mappings over tasks) in order to flexibly reconfigure its behavior, as shown in fig. \ref{poly_meta_map_results}. We train the system to perform a variety of mappings, for example switch the first two inputs of the polynomial, add 3 to the polynomial, or square the polynomial. We then test its ability to generalize to held-out mappings, for example a permutation of the polynomial inputs which it has not encountered before, or an additive shift in the polynomial which it has not been trained on. The system is both able to apply its learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of their application or receiving a natural-language instruction. However, it performs better from examples than language, which is not completely surprising, since the examples provide a richer cue to the task. \par 

@@

%\vspace{-1em}
%\paragraph{Conclusions:}
\section{Conclusions}
In this paper, we've highlighted a new type of flexibility in the form of \emph{meta-mappings}, that is, mappings between tasks. We've suggested that achieving this type of flexibility is difficult in most deep learning architectures, because they separate computation from the knowledge of what is being computed. To address this, we've proposed explicitly representing the tasks by embeddings, and deriving the computation from these embeddings via a HyperNetwork. This allows transformations over task embeddings to transform the system's behavior. To this end, we've proposed a meta-learning system which embeds tasks and data into a shared latent space, and then meta-learns to make mappings over this space. The requisite meta-task sample complexity is small; we showed generalization to unseen meta-mappings after training on only 20 meta-mappings.\par

@@

\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
named\_run\_type & result\_type & mean\_loss & boot\_CI\_low & boot\_CI\_high \\ 
\hline \\[-1.8ex] 
EML & Trained mapping, on trained task & 0.084 & 0.08 & 0.088 \\ 
EML & Trained mapping, on held-out task & 1.664 & 1.345 & 2.077 \\ 
EML & Held-out mapping, on trained task & 1.07 & 0.996 & 1.14 \\ 
EML & Held-out mapping, on held-out task & 1.52 & 1.444 & 1.604 \\ 
Untrained EML network & Trained mapping, on trained task & 13.378 & 12.213 & 14.84 \\ 
Untrained EML network & Trained mapping, on held-out task & 15.469 & 13.778 & 17.303 \\ 
Untrained EML network & Held-out mapping, on trained task & 8.205 & 7.766 & 8.687 \\ 
Untrained EML network & Held-out mapping, on held-out task & 8.625 & 8.165 & 9.127 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\caption{Table for meta-mapping results from examples, figure \ref{poly_meta_map_results_examples}}
\end{table}

\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
named\_run\_type & result\_type & mean\_loss & boot\_CI\_low & boot\_CI\_high \\ 
\hline \\[-1.8ex] 
Language & Trained mapping, on trained task & 0.515 & 0.483 & 0.552 \\ 
Language & Trained mapping, on held-out task & 2.244 & 1.921 & 2.623 \\ 
Language & Held-out mapping, on trained task & 2.072 & 1.958 & 2.19 \\ 
Language & Held-out mapping, on held-out task & 2.35 & 2.254 & 2.447 \\ 
Untrained EML network & Trained mapping, on trained task & 13.328 & 11.977 & 14.823 \\ 
Untrained EML network & Trained mapping, on held-out task & 15.313 & 13.602 & 17.354 \\ 
Untrained EML network & Held-out mapping, on trained task & 8.205 & 7.795 & 8.662 \\ 
Untrained EML network & Held-out mapping, on held-out task & 8.625 & 8.131 & 9.104 \\ 
\hline \\[-1.8ex] 
\end{tabular}
\caption{Table for meta-mapping results from language, figure \ref{poly_meta_map_results_language}}
\end{table}
